---
title: "running_scenarios"
author: "Stefan Rautenbach"
date: "2024-03-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Load packages

```{r libraries, include=FALSE}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(gridExtra)
library(metR)
library(ggpubr)
library(ggfx)
library(RColorBrewer)
library(cowplot)
```

# Source scripts and functions

```{r source, include=FALSE}
source("R/modify_rollout_orderly.R")
source("R/read_and_run_orderly.R")
source("R/cluster_function_orderly.R")
```

# Run scenarios

## Compile Thembisa
This compiles the executable file of thembisa - if this provides errors then the scenarios below will not run

```{r compile, echo = FALSE}
system("g++ -std=c++14 THEMBISA.cpp StatFunctions.cpp mersenne.cpp -o thembisa -O2")
```

## Testing reduction only scenario

These data were used for Figures 1, 3, S1, S2, S3, S4, S12, S13

```{r testing_reduction, include=FALSE}

run_on_cluster(pitc_reduction_years = seq(2025, 2050, 5),
               pitc_reduction_percentage = seq(0,100,5),
               condom_usage_reduction = FALSE,
               condom_usage_decrease = 0,
               condom_decr_start = 2025,
               condom_usage_promotion = FALSE,
               condom_usage_increase = 0,
               condom_incr_start = 2025,
               art_coverage_increase = FALSE,
               art_interrupt_rate_decrease = 0,
               art_incr_start = 2025,
               art_coverage_decrease = FALSE,
               art_interrupt_rate_increase = 0,
               art_decr_start = 2025,
               cumulative_years_list = 50,
               change_mmc = FALSE,
               mmc_rel_rate = 0,
               mmc_change_start = 2025,
               change_prep = FALSE,
               prep_rel_rate = 0, 
               prep_change_start = 2025, 
               summary_name = "test_reduction_only" 
               
)


```

## Testing reduction cost analysis - implemented in 2025

These data were used for Figures 2 and S11

```{r cost analysis data, include=FALSE}

run_on_cluster(pitc_reduction_years = 2025, 
               pitc_reduction_percentage = seq(0,100,25),
               condom_usage_reduction = FALSE,
               condom_usage_decrease = 0,
               condom_decr_start = 2025,
               condom_usage_promotion = FALSE,
               condom_usage_increase = 0,
               condom_incr_start = 2025,
               art_coverage_increase = FALSE,
               art_interrupt_rate_decrease = 0,
               art_incr_start = 2025,
               art_coverage_decrease = FALSE,
               art_interrupt_rate_increase = 0,
               art_decr_start = 2025,
               cumulative_years_list = c(9, 49),
               change_mmc = FALSE,
               mmc_rel_rate = 0,
               mmc_change_start = 2025,
               change_prep = FALSE,
               prep_rel_rate = 0, 
               prep_change_start = 2025, 
               summary_name = "costs" 
               
)

```

## Decreased ART interruption rate & testing reduction - implemented in 2025

These data were used for Figures 4, S5, and S7

```{r decrease art int, include=FALSE}

for (i in seq(0, 14, 0.5)){
  run_on_cluster(pitc_reduction_years = 2025, 
               pitc_reduction_percentage = seq(0,100,5),
               condom_usage_reduction = FALSE,
               condom_usage_decrease = 0,
               condom_decr_start = 2025,
               condom_usage_promotion = FALSE,
               condom_usage_increase = 0,
               condom_incr_start = 2025,
               art_coverage_increase = TRUE,
               art_interrupt_rate_decrease = i,
               art_incr_start = 2025,
               art_coverage_decrease = FALSE,
               art_interrupt_rate_increase = 0,
               art_decr_start = 2025,
               cumulative_years_list = c(50),
               change_mmc = FALSE,
               mmc_rel_rate = 0,
               mmc_change_start = 2025,
               change_prep = FALSE,
               prep_rel_rate = 0, 
               prep_change_start = 2025, 
               summary_name = paste0("art_decrease_", i) 
               
)
}

```

## Increased ART interruption rate & testing reduction - implemented in 2025

These data were used for Figures 4, S5, and S8

```{r increase art int, include=FALSE}
for (i in seq(0, 14, 0.5)){
  run_on_cluster(
               pitc_reduction_years = 2025, 
               pitc_reduction_percentage = seq(0,100,5),
               condom_usage_reduction = FALSE,
               condom_usage_decrease = 0,
               condom_decr_start = 2025,
               condom_usage_promotion = FALSE,
               condom_usage_increase = 0,
               condom_incr_start = 2025,
               art_coverage_increase = FALSE,
               art_interrupt_rate_decrease = 0,
               art_incr_start = 2025,
               art_coverage_decrease = TRUE,
               art_interrupt_rate_increase = i,
               art_decr_start = 2025,
               cumulative_years_list = c(50),
               change_mmc = FALSE,
               mmc_rel_rate = 0,
               mmc_change_start = 2025,
               change_prep = FALSE,
               prep_rel_rate = 0, 
               prep_change_start = 2025,
               summary_name = paste0("art_increase_", i)
               ) 
}


```

## Increased probability of condom usage & testing reduction - implemented in 2025

These data were used for Figures 5, S6, and S9

```{r increase condom, include=FALSE}
for (i in seq(0, 14, 0.5)){
  run_on_cluster(pitc_reduction_years = 2025, 
                 pitc_reduction_percentage = seq(0,100,5),
                 condom_usage_reduction = FALSE,
                 condom_usage_decrease = 0,
                 condom_decr_start = 2025,
                 condom_usage_promotion = TRUE,
                 condom_usage_increase = i,
                 condom_incr_start = 2025,
                 art_coverage_increase = FALSE,
                 art_interrupt_rate_decrease = 0,
                 art_incr_start = 2025,
                 art_coverage_decrease = FALSE,
                 art_interrupt_rate_increase = 0,
                 art_decr_start = 2025,
                 cumulative_years_list = c(50),
                 change_mmc = FALSE,
                 mmc_rel_rate = 0,
                 mmc_change_start = 2025,
                 change_prep = FALSE,
                 prep_rel_rate = 0, 
                 prep_change_start = 2025, 
                 summary_name = paste0("condom_increase_",i) 
                 
  )
}
```

## Decreased probability of condom usage & testing reduction - implemented in 2025

These data were used for Figures 4, S5, and S10

```{r decrease condom, include=FALSE}
for (i in seq(0, 14, 0.5)){
  run_on_cluster(pitc_reduction_years = 2025, 
                 pitc_reduction_percentage = seq(0,100,5),
                 condom_usage_reduction = TRUE,
                 condom_usage_decrease = i,
                 condom_decr_start = 2025,
                 condom_usage_promotion = FALSE,
                 condom_usage_increase = 0,
                 condom_incr_start = 2025,
                 art_coverage_increase = FALSE,
                 art_interrupt_rate_decrease = 0,
                 art_incr_start = 2025,
                 art_coverage_decrease = FALSE,
                 art_interrupt_rate_increase = 0,
                 art_decr_start = 2025,
                 cumulative_years_list = c(50),
                 change_mmc = FALSE,
                 mmc_rel_rate = 0,
                 mmc_change_start = 2025,
                 change_prep = FALSE,
                 prep_rel_rate = 0, 
                 prep_change_start = 2025, 
                 summary_name = paste0("condom_decrease_",i) 
                 
  )
}
```